Testing atlantisom: generate survey sampled length comps for Norwegian Barents Sea Atlantis

### 2019-05-14 visualization_Rmd/NEUSStdSurvLengthCompTest.Rmd
initial lf sample viz NOBA NEUS

---
title: "Testing atlantisom: generate survey sampled length comps for California Current Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

atf_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
atf_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
atf_resnstd <- resnstd[resnstd$species == "Arrowtooth_flounder",]

atf_length_stdsurv <- calc_age2length(structn = atf_structnstd,
                                 resn = atf_resnstd,
                                 nums = atf_numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

```{r atflengthsamp1-test}

lfplot <- ggplot(atf_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, atf_length_stdsurv$natlength$species))

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

## Samples for all species from SAVED file

@@

```{r allspplengthsamp, eval=FALSE, echo=TRUE}

@@

Runtime for census lengths was 5.5 hours for CCA. For standard survey lengths runtime was not reduced because the dimensions (species, timesteps) were identical.

Compare sampled lf with census from [here](https://sgaichas.github.io/poseidon-dev/CCATrueLengthCompTest.html):

@@

# select a species
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

ss_length_stdsurv <- length_stdsurv$natlength %>%
  filter(species == "Herring")

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, lf_census_prop$species))

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

>>>>

---
title: "Testing atlantisom: generate survey sampled length comps for Northeast US  Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

ss_numsstd <- numsstd[numsstd$species == "SkateRay",]
ss_structnstd <- structnstd[structnstd$species == "SkateRay",]
ss_resnstd <- resnstd[resnstd$species == "SkateRay",]

ss_length_stdsurv <- calc_age2length(structn = ss_structnstd,
                                 resn = ss_resnstd,
                                 nums = ss_numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

```{r sslengthsamp1-test}

lfplot <- ggplot(ss_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_stdsurv$natlength$species))

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

## Samples for all species and SAVE the file

@@

```{r allspplengthsamp, echo=TRUE}

@@

Runtime for census lengths was <1 hour for NEUS because it is a 50 year run and we are taking lengths only once per year. For standard survey lengths runtime was not reduced because the dimensions (species, timesteps) were identical.

Compare sampled lf with census from [here](https://sgaichas.github.io/poseidon-dev/NEUSTrueLengthCompTest.html):

@@

# select a species
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Planktiv_S_Fish")

ss_length_stdsurv <- length_stdsurv$natlength %>%
  filter(species == "Planktiv_S_Fish")

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, lf_census_prop$species))

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

### 2019-05-14 visualization_Rmd/NOBAStdSurvLengthCompTest.Rmd
initial lf sample viz NOBA NEUS

---
title: "Testing atlantisom: generate survey sampled length comps for Northeast US  Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

ss_numsstd <- numsstd[numsstd$species == "SkateRay",]
ss_structnstd <- structnstd[structnstd$species == "SkateRay",]
ss_resnstd <- resnstd[resnstd$species == "SkateRay",]

@@

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

Runtime for census lengths was <1 hour for NEUS because it is a 50 year run and we are taking lengths only once per year. For standard survey lengths runtime was not reduced because the dimensions (species, timesteps) were identical.

Compare sampled lf with census from [here](https://sgaichas.github.io/poseidon-dev/NEUSTrueLengthCompTest.html):

@@

# select a species
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Planktiv_S_Fish")

ss_length_stdsurv <- length_stdsurv$natlength %>%
  filter(species == "Planktiv_S_Fish")

>>>>

---
title: "Testing atlantisom: generate survey sampled length comps for Norwegian Barents Sea Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

ss_numsstd <- numsstd[numsstd$species == "Green_halibut",]
ss_structnstd <- structnstd[structnstd$species == "Green_halibut",]
ss_resnstd <- resnstd[resnstd$species == "Green_halibut",]

@@

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

Runtime for census lengths was ~2.5 hours for NOBA once we decided once per year was plenty. For standard survey lengths runtime was not reduced because the dimensions (species, timesteps) were identical.

Compare sampled lf with census from [here](https://sgaichas.github.io/poseidon-dev/NOBATrueLengthCompTest.html):

@@

# select a species
ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Norwegian_ssh")

ss_length_stdsurv <- length_stdsurv$natlength %>%
  filter(species == "Norwegian_ssh")
